Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-08-13 Manuscript/HI_Model_ms.Rmd
updated manuscript and response letter files

The data that support the findings of this study are openly available. LUCAS model tabular output data and metadata are available in machine readable format from  USGS ScienceBase at https://doi.org/10.5066/P9AWLFKZ. LUCAS model input data and R scripts used to format input data, summarize output data, and compile this manuscript are available at https://doi.org/10.5281/zenodo.5198072.

>>>>

The data that support the findings of this study are openly available. LUCAS model tabular output data and metadata are available in machine readable format from  the USGS ScienceBase repository at https://doi.org/10.5066/P9AWLFKZ. LUCAS model input data and R scripts used to format input data, summarize output data and compile this manuscript are available from a GitHub repository (https://github.com/selmants/HI_Model) archived at https://doi.org/10.5281/zenodo.5198072.
